THESIS PROJECT PROPOSAL

### 2019-11-14 project_ashish/paper.tex

%% 
%% Copyright 2016 Icm Ltd
\documentclass[final,3p]{CSP}
\usepackage{amssymb}
\usepackage{changepage}
\usepackage{float}
\begin{document}

\begin{frontmatter}

\title{THESIS PROJECT PROPOSAL}

\author[]{Ashish Sehrawat$^a$}
\author[]{Dr. Jose Feliciano Benitez Rubio$^b$}

%\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
%\cortext[mycorrespondingauthor]{Corresponding author}
%\ead{support@Icm.com}

\address[mymainaddress]{Universidad de Sonora}
%\address[mysecondaryaddress]{Universidad de Sonora}

\begin{keyword}\rm
\begin{adjustwidth}{2cm}{2cm}{\itshape\textbf{Keyword:}}  
Higgs boson, Higgs boson production, Higgs boson decay, Higgs boson coupling, 
\end{adjustwidth}
\end{keyword}

\begin{keyword}\rm
\begin{adjustwidth}{2cm}{2cm}{\itshape\textbf{Title:}}  
Study of the Higgs boson production in association with a single top quark in proton collisions at the Large Hadron Collider.
\end{adjustwidth}
\end{keyword}

\begin{abstract}\rm
% \begin{adjustwidth}{2cm}{2cm}{
\itshape\textbf{Abstract:}
The abstract
%\end{adjustwidth}
\end{abstract}

\end{frontmatter}

\section{BACKGROUND}

@@

The expected results of this project are the following:
• Improve data adjustments and study the effects of uncertainties.
• Improve the sensitivity to the tH signal in the data of the second CMS run.
• Limit calculations in the effective section incorporating data from the second
run of the LHC.
• Calculate projections of signal sensitivity for the different phases of the LHC.

@@

\appendix
\section{SKILLS THAT WILL BE DEVELOPED}
The following are skills that will be developed based on the work on this project:
- understand particle physics from an experimental point of view.
- analyze and manipulate data using modern programming languages such as C++, Python and ROOT.
- data analysis techniques.
- use high performance computing.

>>>>

\documentclass[final,3p]{CSP}
\usepackage{amssymb}
\usepackage{changepage}
\usepackage{float}
\usepackage{fancyhdr}
%\usepackage[margin=1in,headsep=.2in]{geometry}

\pagestyle{fancy}
\fancyhf{}
\rhead{Thesis Project Proposal}
\lhead{Ashish Sehrawat}
\rfoot{Page \thepage}

\setlength{\headsep}{0.2in}

\begin{document}

%\begin{frontmatter}
%\title{THESIS PROJECT PROPOSAL}  
%\author[]{Ashish Sehrawat$^a$}
%\author[]{Dr. Jose Feliciano Benitez Rubio$^b$}
%\cortext[mycorrespondingauthor]{Corresponding author}
%\ead{support@Icm.com}
%\address[mymainaddress]{Universidad de Sonora}
%\begin{keyword}\rm
%\begin{adjustwidth}{2cm}{2cm}{\itshape\textbf{Keyword:}}  
%Higgs boson, Higgs boson production, Higgs boson decay, Higgs boson coupling, 
%\end{adjustwidth}
%\end{keyword}
%\begin{keyword} \rm
%\end{keyword}
%\begin{abstract}\rm
%\end{abstract}
%\end{frontmatter}

\begin{titlepage}
	\centering
        {\scshape\Large THESIS PROJECT PROPOSAL\par}

	\vspace{2cm}
        \begin{adjustwidth}{2cm}{2cm}{
            TITLE:\par
            \large{Study of the Higgs boson production in association with a single top quark in proton collisions at the Large Hadron Collider}\par}
        \end{adjustwidth}

	\vspace{0.5cm}
        \begin{adjustwidth}{2cm}{2cm}{
            RESEARCH LINE: \par
            Astrof\'{i}sica, Cosmolog\'{i}a y F\'{i}sica de Part\'{i}culas \par}
        \end{adjustwidth}

        \vspace{4cm}
        {\underline{\hspace{8cm}}\par}
	{\scshape\large Ashish Sehrawat\par}
        {Student\par}

        \vspace{1cm}
        {\underline{\hspace{8cm}}\par}
	{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio\par}
        {Director\par}

        \vspace{1cm}
        {Program: Doctorado en Ciencias (F\'{i}sica) \par}
        {Departamento de Investigac\'{i}on en Fis\'{i}ca (DIFUS) \par}
        {Universidad de Sonora \par}

        \vfill
	{\today}

\end{titlepage}

\newpage
{
\hspace{0pt}
\vfill
\centering

  \begin{adjustwidth}{2cm}{2cm}{\large Study of the Higgs boson production in association with a single top quark in proton collisions at the Large Hadron Collider\par}
    \vspace{1cm}
    \centering
    {\itshape\textbf{Abstract:}\par}
    The abstract \par
  \end{adjustwidth}

\hspace{0pt}
\vfill
}

%\centering Ashish Sehrawat
%\newline \newline
%\centering Director: Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio
%\newline \newline
%Posgrado en Ciencias (Fis\'{i}ca)
%\newline 
%Departamento de Investigac\'{i}on en Fis\'{i}ca (DIFUS)
%\newline 
%Universidad de Sonora
%\newline \newline
%\today

\newpage
\section{BACKGROUND}

@@

The expected results of this project are the following:
- Improve data adjustments and study the effects of uncertainties.
- Improve the sensitivity to the tH signal in the data of the second CMS run.
- Limit calculations in the effective section incorporating data from the second run of the LHC.
- Calculate projections of signal sensitivity for the different phases of the LHC.

\section{SKILLS THAT WILL BE DEVELOPED}
The following are skills that will be developed based on the work on this project:
- understand particle physics from an experimental point of view.
- analyze and manipulate data using modern programming languages such as C++, Python and ROOT.
- data analysis techniques.
- use high performance computing.

@@
